A Constraint Solving Approach to Parikh Images of Regular Languages

### 2024-02-29 introduction.tex
Mention results in introduction
Closes: #87

We implement \Calculus{} as a plug-in theory for the \Princess{} automated
theorem prover.
% Suggestions: l87-89, l102-103: Mention the main evaluation result; such as, x% more than baseline.
%
We additionally wrap the Parikh image solver as a stand-alone tool, \Catra.
\Catra{} also supports a variant of the approximate method of~\cite{approximate-parikh}, its fall-back variant adapted
from~\cite{generate-parikh-image}, and an adapter for the \Nuxmv{} model
checker~\cite{nuxmv}. Using \Catra, we compare \Calculus{} to the other two
back-ends on \NrBenchmarks{} distinct Parikh automata intersection problems
generated by \OstrichPlus{} when solving the PyEx string constraint benchmark
suite involving string length constraints~\cite{pyex}.

>>>>

We implement \Calculus{} as a plug-in theory for the \Princess{} automated
theorem prover and experimentally use it as the Parikh image interesection solver for
to the \Ostrich{} string constraint solver.

We additionally wrap the Parikh image solver as a stand-alone tool, \Catra{}.
\Catra{} also supports a variant of the approximate method of~\cite{approximate-parikh}, its fall-back variant adapted
from~\cite{generate-parikh-image}, and an adapter for the \Nuxmv{} model
checker~\cite{nuxmv}. Using \Catra, we compare \Calculus{} to the other two
back-ends on \NrBenchmarks{} distinct Parikh automata intersection problems
generated by \OstrichPlus{} when solving the PyEx string constraint benchmark
suite involving string length constraints~\cite{pyex}, finding that \Calculus{}
outperforms both \Nuxmv{} and the baseline method, allowing \Calculus{}
to solve every problem solved by baseline within \numprint{30}s in under \numprint{5}s.
\Calculus{} in particular outperforms \Nuxmv{} on unsatisfiable instances, more than 
doubling the number of unsatisfiable results found within a \numprint{30}s timeout.

We extend the \Ostrich{} string solver's backend portfolio with \Calculus{} via
\Catra{} as the Parikh image intersection solver of the \OstrichPlus{}~algorithm,
obtaining improvements in both \textsc{Sat}  and \textsc{Unsat} performance in
\Ostrich{}' results from SMT-COMP 2023, crucially allowing \Ostrich{} to win
the unsatisfiable category of the track of quantifier-free, linear constraints
over string logic (QF\_SLIA) and increasing the number of \textsc{Sat}~results
by \numprint{3}\%.
